Graph Exploration and Search

### 2017-11-14 paper.tex
keyword search

The research on graph exploration has revolved around three main pillars: \emph{keyword graph queries}, \emph{exploratory graph analysis}, and \emph{refinement of query results}

@@

\stitle{Keyword Graph Queries} \dnote{(Yinghui)}

>>>>

The research on graph exploration has revolved around three main pillars: \emph{keyword graph queries}, \emph{exploratory graph analysis}, and \emph{refinement of query results}.

@@

\stitle{Keyword Graph Queries}  %\dnote{(Yinghui)} 
applies user-friendly keyword queries to explore a targeted graph. 
The query answers are usually defined as subgraphs that contain 
the nodes and edges with information specified by the query terms. 
New keywords can be suggested from observed answers and are used to expand the 
original queries, which triggers a new round of query evaluation. 
Keyword queries are desirable for end users who do not have 
prior knowledge of underlying graph data, for which writing a 
complex graph query (e.g., SPARQL) is difficult. On the other hand, 
keywords can be ambiguous. While keyword search has been extensively studied, 
the major research effort in this category focuses 
on disambiguation and keyword query refinement.
